Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-01-28 paper/main.tex
Updates

\section{Background and Related Work}
\label{sec:background}
We consider random variables $ X $ and $ Y $ with a possible multi-dimensional
variable $ \bm{Z} = \{ Z_1, \cdots, Z_k \} $. We consider these variables in
the mixed data setting where these variables can be any combination of
continuous, categorical, or ordinal unless specified. We also assume all
variables to be observed. We use $ \rvert \bm{Z} \rvert $ to represent the
cardinality of the variable $ \bm{Z} $. We write $ \bm{x} = (x_1, \cdots, x_n)
$ for a sample from $ X $ of size $ n $. We write the expectation of a variable
$ X $ as $ \mathbb{E}[X] $, conditional expectations as $ \mathbb{E}[X |
\bm{Z}] $.

@@

>>>>

\section{Background and Related Work}
\label{sec:background}
\subsection{Notations}
We consider random variables $ X $ and $ Y $ with a possible multi-dimensional
variable $ \bm{Z} = \{ Z_1, \cdots, Z_k \} $. We consider these variables in
the mixed data setting where these variables can be any combination of
continuous, categorical, or ordinal unless specified. We also assume all
variables to be observed. We use $ \rvert \bm{Z} \rvert $ to represent the
cardinality of the variable $ \bm{Z} $. We write $ \bm{x} = (x_1, \cdots, x_n)
$ for a sample from $ X $ of size $ n $. We write the expectation of a variable
$ X $ as $ \mathbb{E}[X] $, conditional expectations as $ \mathbb{E}[X |
\bm{Z}] $.

@@

So, in a sense this measure generalized currently used measures of associations
to mixed data.
